Equivalence Hypergraphs: E-Graphs for Monoidal Theories

### 2023-12-20 sections/combinatorial_semantics.tex
Soundness and fullness for PROP(\Sigma)+

\update{Naturality and SMC laws are implied by $+$ being a coproduct[reference?]}.

@@

\begin{definition}[Category $\;\catname{Csp_{D}(Hyp_{\Sigma})}$]
\label{def:cspd}
Category $\catname{Csp_{D}(Hyp_{\Sigma})}$ is a \textit{full} sub-category of $\catname{Csp(Hyp_{\Sigma})}$ which has discrete hypergraphs as objects.
\update{Assuming that $D$ is a functor from PROP to $\catname{Hyp_{\Sigma}}$, $\catname{Csp_{D}(Hyp_{\Sigma})}$ is also a PROP and hence an SMC (Theorem 3.6~\cite{Frobenius}).}
\end{definition}

@@

    \update{Looks fine?}

@@

% Note that if $s : e_1 \mapsto \{v_1,v_2\}$ and $s : e_2 \mapsto \{v_3,v_4\}$  and $e_1 \sim e_2$ then $\sfrac{s}{\sim R} : [e_1,e_2] \to \{[v_1,v_3],[v_2,v_4]\}$ because $f$ and $g$ are homomorphisms.
% Then, $\sfrac{i_1}{\sim R}$ maps $y \in Y$ to its equivalence class and likewise for $\sfrac{i_2}{\sim R}$.
% we will denote the equivalence classes in $\sfrac{X + Y}{\sim R}$ as $[x]$ and $[y]$ depending on their pre-image being either in $X$ or $Y$.
% Before we procced, we need to show that $\sfrac{i_1}{\sim R}$ and $\sfrac{i_2}{\sim R}$ are homomorphisms.
% Let $e_{x}$ be an edge in $X$ and $v_x$ is its source. We need to check that $\sfrac{i_1}{\sim R}(v_x) = (\sfrac{i_1}{\sim R};\sfrac{s_{X}}{\sim R})(e_x)$.
% $\sfrac{i_1}{\sim R}(v_x) = [v_x]$ and $(\sfrac{i_1}{\sim R};\sfrac{s_{X}}{\sim R})(e_x) = \sfrac{s_{X}}{\sim R}([e_x]) = [v_x]$ and hence $\sfrac{i_1}{\sim R}$ is a homomorphism, simialrly $\sfrac{i_2}{\sim R}$ is.
Now, the square obviously commutes.
To show that $\sfrac{X + Y}{\sim}$ is a pushout we need to argue that for each $Q$ and morphisms $j_1 = (j_{1,V}, j_{1,E})$ and $j_2 = (j_{2,V}, j_{2,E})$ such that the above square commutes there is a unique $u = (u_{V}, u_{E})$ such that $j_1 = \sfrac{i_{1}}{\sim} ; u$ and $j_2 = \sfrac{i_2}{\sim} ; u$.
We will define such $u$ as $u_{E}([i_{1,E}(e_{x})]) = j_{1,E}(e_{x})$ and $u_{E}([i_{2,E}(e_{y})]) = j_{2,E}(e_y)$ (similarly for $u_{V}$) and claim that it is a well-defined function by showing that if $t_1 \sim t_2$ then $u_{E}(t_1) = u_{E}(t_2)$.
There are three options analogoues to the proof above, so we will show the base case for $t_1 = i_{1,E}(e_{x})$ and $t_2 = i_{2,E}(e_{y})$.
$t_1 \sim t_2$ implies that there exists at least one $z$ in $E_{Z}$ such that $i_{1,E}(e_{x}) = f_{E};i_{1,E}(z)$ (or $e_{x} = f_{E}(z)$) and $[i_{1,E}(e_{x})] = \sfrac{i_{1,V}}{\sim}(e_x)$, and $e_y = g_{E}(z)$ $[in_{2,E}(e_{y})] = \sfrac{i_{2,V}}{\sim}(e_y)$.
By applying $j_{1,E}$ to the first we get $j_{1,E}(f_{E}(z)) = j_{1,E}(e_x)$ and similarly for $j_{2,E}$: $j_{2,E}(g_{E}(z)) = j_{2,E}(e_y)$ and $j_{1,E}(e_{x}) = j_{2,E}(e_{y})$ by commutativity.
Hence, $u_{E}([in_{1,E}(e_x)]) = u_{E}([in_{2,E}(e_y)])$.
\update{Above $e_x$ and $e_y$ are different from $e_x$ and $e_y$ from the first proof, i.e. they are in $E_{X}$ and $E_{Y}$. This is probablty not good.}

\question{Next, $u$ is a homomorphism because $j_1$ and $j_2$ are.}
Finally, $u$ is unique.
Assume, that there exists $w : \sfrac{X+Y}{\sim R} \to Q$ for the same $j_1$ and $j_2$.
In order for them to commute $w_{E}([i_{1,E}(x)]) = j_1(x)$ and $w([in_{2,E}(y)]) = j_2(y)$ (similarly for $w_{V}$) which is the same as $u_{E}$.
That is, $j_1$ and $j_2$ determine $u$ uniquely.

@@

    An e-hypergraph $\mathcal{G}$ over a monoidal signature $\Sigma$ is a tuple \[(V_{\mathcal{G}},E_{\mathcal{G}},s,t,l,<_c,\#)\] where $(V_{\mathcal{G}},E_{\mathcal{G}},s,t)$ are the same as in~\ref{def:hypergraph}.
    The labelling $l$ is modified to include an extra value $\bot \;$ $l :E_{\mathcal{G}} \to \Sigma + 1$. 
    % With an abuse of notation, we will confuse $\mathcal{G}$ with $V_{\mathcal{G}} \cup E_{\mathcal{G}}$, when treating it as a set.
    \question{Shall I use $\cup$ instead of $+$?}
    $<_c \subset (V_\mathcal{G} + E_\mathcal{G}) \times (V_\mathcal{G} + E_\mathcal{G})$ is a child relation imposing a strict partial order on $(V_\mathcal{G} + E_\mathcal{G})$.
    We require that for a given $x \in (V_\mathcal{G} + E_\mathcal{G})$ a set of all predecessors of $x\;$ $[x) = \{x' \in E_\mathcal{G} \;||\; x' <_c x\; \}$ is finite and consists of edges $e \in E_{\mathcal{G}}$ such that $l(e) = \bot$ only.
    Next, each $x$ has at most one immediate predecessor.
    \update{We will denote the fact that $e$ is an immediate predecessor of $v$ as $e <_c^{\mu} v$.}
    Similarly, a set of all successors is $(x] = \{x' \in (V_\mathcal{G} + E_\mathcal{G}) \; ||\; x <_{c} x'\}$ where $x'$ can be a node or an edge. 
    % An edge $e \in E_{\mathcal{G}}$ is unlabelled, i.e. $l(e) = \bot$ iff $(e] \not = \varnothing$.
    Finally, we require that $<_c^{\mu}$ respects connectivity, i.e. if $v \in s(e)$ then $e' <_c^{\mu} e$ iff $e' <_c^{\mu} v$.

@@

    \item \[
        \phi_{E}(<_{c,\mathcal{F}}^{\mu}(i_{V_{\mathcal{F}}}(x))) = <_{c,\mathcal{G}}^{\mu}(\phi_{V};i_{V_{\mathcal{G}}}(x))
        \] when $x$ is a node,
        and
        \[
        \phi_{E}(<_{c,\mathcal{F}}^{\mu}(i_{E_{\mathcal{F}}}(x))) = <_{c,\mathcal{G}}^{\mu}(\phi_{E};i_{E_{\mathcal{G}}}(x))  
        \] when $x$ is an edge.
          \update{We do not require such an equation when $[x) = \varnothing$}.

@@

    \begin{enumerate}
    \item $Z$ is a \textit{discrete} e-hypergraph, i.e. it has no edges.
    \item $[f_{V}(v_i)) = [f_{V}(v_j))$ and $[g_{V}(v_i)) = [g_{V}(v_j))$ for all $v_i,v_j \in V_{Z}$. \update{This essentially means that $f,g$ do not map nodes to levels of different hierarchy.}
    \item If $[f_{V}(v)) \not = \varnothing$ then $[g_{V}(v)) = \varnothing$ and vice versa.
    \item $\consistency^{\mu}(f(v_i)) = \consistency^{\mu}(f(v_j))$ and $\consistency^{\mu}(f(g_i)) = \consistency^{\mu}(g(v_j))$.
    \item $f$ and $g$ are mono.
    \label{pushout:assumptions}
    \end{enumerate}

@@

              \update{Assumptions above guarantee that the predecessor of such node does not depend on the choice of $e$ if there are several of them.}

@@

    \question{In the case when images of $f$ and $g$ are top-level the function is undefined. Shall we introduce bottom?}

@@

    \update{We will also build this relation in steps, first we do steps for nodes (1) - (3), then step (1) for edges and finally, we will interleave step (2) for edges and step (4) for nodes until fixed point.

@@

    }

@@

    where
    \begin{enumerate}
        \item $A \in \text{obj}(\catname{EHyp_{\Sigma}})$
        \item $W, X, Y, Z$ are discrete and $f,g,h,k$ are monos
        \item \update{The image of $f;g$ (respectively, $k;h$) constitutes of nodes $v$ such that $[v) = \varnothing$}
    \end{enumerate}
    Since $f$ and $k$ are monos, $W$ and $Z$ are essentially subgraphs of $X$ and $Y$ and hence we will introduce the following notation which better depicts that such cospans are effectively e-hypergraphs with \textit{external} interfaces

@@

\[
    k = \langle b;p_2, f|_{Y \setminus Y_{ext}};p_1 \rangle
\]
\update{I've put copairings above}
% \[
% \begin{tikzcd}
% Y_{ext} \arrow[d] & 0 \arrow[l] \arrow[d]    \\
% Y'          & Y' \setminus Y_{ext} \arrow[l]
% \end{tikzcd}
% \]

@@

\update{Similarly to~\ref{def:cspd} this category has a symmetric monoidal product given by a coproduct in $\catname{EHyp_{\Sigma}}$ which makes it into an SMC if $D$ is a functor from PROP to $\catname{EHyp_{\Sigma}}$.}
More precisely, below are cospans for tensor product and symmetry.
Tensor unit is given by the initial object in $\catname{EHyp_{\Sigma}}$.

@@

% https://q.uiver.app/#q=WzAsNSxbMCwwLCJYICsgWSJdLFsyLDAsIlggKyBZIl0sWzQsMCwiWSArIFgiXSxbNiwwLCJZICsgWCJdLFs4LDAsIlkgKyBYIl0sWzAsMSwiaWRfWCArIGlkX1kiXSxbMSwyLCJcXHNpZ21hX3tYLFl9Il0sWzQsMywiaWRfWSArIGlkX1giLDJdLFszLDIsImlkX1kgKyBpZF9YIiwyXV0=
\[
\adjustbox{scale=0.75, center}{
\begin{tikzcd}
	{X + Y} && {X + Y} && {Y + X} && {Y + X} && {Y + X}
	\arrow["{id_X + id_Y}", from=1-1, to=1-3]
	\arrow["{\sigma_{X,Y}}", from=1-3, to=1-5]
	\arrow["{id_Y + id_X}"', from=1-9, to=1-7]
	\arrow["{id_Y + id_X}"', from=1-7, to=1-5]
\end{tikzcd}
}
\]\label{morphism:symmetry}

\question{Or shall we say that symmetry is inherited from $\catname{EHyp_{\Sigma}}$ because coproduct is commutative and associative?}
\end{definition}

@@

\begin{remark}
    Pushout for composition is computed by first taking a coproduct of $A$ and $B$ and then identifying the nodes that share the same pre-image in $Y_{ext}$.
    Consider an example in Figure~\ref{fig:e-hyp_composition_example} below.
    The pushout is depicted in Figure~\ref{fig:e-hyp_composition_example_2}.
    New interfaces are shown in Figure~\ref{fig:e-hyp_composition_example_3}.
    They are computed as shown: a disjoint union of the input interface of the left component of the composition with the input interface of the right component of the composition except for the nodes in the image of the outermost output interface of the left component is taken.
    Similarly for the output interface.
    In particular, $\{0,1,2,3\} \uplus (\{6,7,8,9,10\} \setminus \{6\}) = \{0,1,2,3,7,8,9,10\}$.
    % The conflict and child relations in the pushout are a disjoint union of the corresponding relations from pushout components.
    \update{Note that pushout for such composition always exists as the interface in the middle is descrete and nodes in the images of the middle interface are at the outermost level as well.
    Furthermore, $f_{ext};f$ and $g_{ext};g$ are monos and hence the span satisfies our assumptions.
    }
\end{remark}

@@

\update{below definition depends on whether we require the homomorphism to reflect the conflicts}

@@

\begin{figure}
    \[
    \scalebox{0.75}{
    \tikzfig{combinatorial_semantics/f_plus_g_new}
    }
    \]
    \caption{$+$ of two morphisms in $\Ecospans$}
    \label{fig:A+B}
\end{figure}

@@

\update{We can probably omit the proofs below because they are obvious. But keeping them here serves as a sanity check.}

@@

    This category is also symmetric monoidal and has $+$ by the lemma above.
\end{definition}

@@

\update{I have run out of possible names for a category}

@@

        \update{I will try to reinvent a similar proof from~\cite{Frobenius2} as the cited proof does not make sense to me}

@@

    \update{Can we check the proof? I haven't used all the conditions from monogamous-ness above.
    Although, if the morphism $i+j \to L$ is mono, the complement is unique for not-monogamous hypergraphs as well.}

@@

\question{
\begin{definition}[Convex down-closed match] 
    We call $m : L \to G$ in $\catname{EHyp_{\Sigma}}$ a convex down-closed match if

    \begin{enumerate}
        \item $m$ is monomorphism
        \item $m(L)$ is a convex down-closed subgraph of $G$
        \item \update{I've removed the requirement that consistency should be reflected because well typedness prohibits otherwise formed matches.}
    \end{enumerate}
\end{definition}
}

@@

\Aleksei{Do we need to introduce substitution? This is needed if our rewrite rules are going to have variables as labels.}

@@

\Aleksei{Check the proof}

\Aleksei{Can we reuse anything from~\cite{Frobenius}?}

Consider an example below that illustrates the introduced constraints.

\update{I've switched to $[ \cdot ]$ for our functor to be able to differenciate between $\llbracket \cdot \rrbracket$, $\llangle \cdot \rrangle$}
\begin{remark}
    For now, we will informally denote a combinatorial interpretation of a morphism $f$ in $\textsf{PROP}^{+}(\Sigma)$ as $[ f ]$.
\end{remark}

A DPOI square for rewriting in $\WellTypedMdaEcospans$ is depicted in Figure~\ref{fig:refined_dpoi}.
A projection rule of $\llbracket f + g \rrbracket \to \llbracket f \rrbracket$ is shown in the top half of the diagram.
The image of the matching $m$ is shown in red and its image is a convex down-closed e-hypergraph.
Pushout complement is then computed by removing the image of $m$ from the target e-hypergraph by keeping intact the nodes that have a pre-image in the carrier of the rewriting span. The corresponding mda-cospan is depicted at the bottom: $c_i = g_i \setminus (l_i \setminus i) = \{18, 19, 1, 2, 13, 14, 5, 6, 7, 8\} \setminus (\{1,2,5,6,7,8\} \setminus \{1,2\}) = \{18, 19, 1, 2, 13, 14, 5, 6, 7, 8\} \setminus \{5,6,7,8\} = \{18,19,1,2,13,14\}$ and $c_i + j = \{18,19, 1, 2, 13, 14, 3, 4\}$ which is the input interface for $C$. Similar computations are performed for $c_o$. Then pushout glues $R$ and $C$ together along $i + j$ and the resulting interface $h_i = c_i + (r_i \setminus i) = \{18,19, 1, 2, 13, 14\} + \varnothing = \{18,19, 1, 2, 13, 14\}$ and likewise for $h_o$.

@@

\end{example}

\Aleksei{This figure yeilds "Dimension too large". Need to fix it.}

Unlike SMC equations the equations for semilattice enriched categories are not absorbed by e-hypergraph representation and hence to further build a correspondence between $\textsf{PROP}^{+}(\Sigma)$ and $\WellTypedMdaEcospans$ we add them as structural rewrite rules.
Recall that the category $\catname{EHyp_{\Sigma}}$ does not have all pushouts and hence we need to explicitly show that the pushouts that we need exist.

\begin{proposition}
Pushouts for all semilattice enrichment equations exist.

\begin{proof}
    Let us give a combinatorial interpretation for an instance of the first equation (distributivity) in~\ref{fig:string-equations}.
    It can be found in Figure~\ref{fig:distributivity_interpretation}.
    After we identify a convex down-closed image of the left-hand side of this rule within a graph $G$ we remove the image by keeping only the outermost nodes.
    Then we simply glue the right-hand side of the rule into the hole.
    Since we glue along the outermost nodes this does not introduce any conflict with regard to child relation.
    Such equations are not absorbed by e-hypergraph representation unlike SMC equations because the right-hand side contains more edges, i.e. graphs $G$ and $H$ are not isomorphic.
    Similar argument applies to other rules as well.

\end{proof}
\end{proposition}

\update{I think I haven't paid any attention to this fact previously, but it seems that in~\cite{Frobenius} the functor $\llbracket - \rrbracket$ is between $PROP_{\Sigma_{Frob}}$ and $Csp_{D}(Hyp_{\Sigma})$, i.e. PROP is quotiented by Frobenius equations, but they are absorbed in hypergraphs domain. We will have a similar thing: $\llbracket - \rrbracket: PROP^{+}_{\Sigma^{+}} \to \WellTypedMdaEcospans_{R^+}$, i.e. we will quotient PROP$^{+}$ by semilattice equations and quotient e-hypergraphs by the interpretation of these equations as they are not absorbed. The quotienting on the left is always implicit?}

\begin{figure}
    \centering
    \[
    \scalebox{0.45}{
    \tikzfig{combinatorial_semantics/structural_rule_pushout}}\]  
    \caption{Distributivity rewrite rule interpretation}
    \label{fig:distributivity_interpretation}
\end{figure}

\begin{definition}
    We will denote with $\mathcal{S}$ the interpretation of the equations in~\ref{fig:string-equations} as rewrite rules in $\WellTypedMdaEcospans$.
    In particular, for all $l = r$ in~\ref{fig:string-equations}, $\mathcal{S}$ will contain $\langle [l], [r]\rangle$ and $\langle [r], [l] \rangle$.
    \update{Technically we add those for all possible instances of $l$ and $r$ in~\ref{fig:string-equations}.}
\end{definition}

>>>>

This construction turns this data into a symmetric monoidal category~\cite{MonoidalCoproduct}.

@@

\begin{definition}[Category $\;\catname{Csp_{D}(Hyp_{\Sigma})}$]
\label{def:cspd}
Category $\catname{Csp_{D}(Hyp_{\Sigma})}$ is a \textit{full} sub-category of $\catname{Csp(Hyp_{\Sigma})}$ which has discrete hypergraphs as objects.
% \update{Assuming that $D$ is a functor from PROP to $\catname{Hyp_{\Sigma}}$, $\catname{Csp_{D}(Hyp_{\Sigma})}$ is also a PROP and hence an SMC (Theorem 3.6~\cite{Frobenius}).}
\end{definition}

@@

@@

% Note that if $s : e_1 \mapsto \{v_1,v_2\}$ and $s : e_2 \mapsto \{v_3,v_4\}$  and $e_1 \sim e_2$ then $\sfrac{s}{\sim R} : [e_1,e_2] \to \{[v_1,v_3],[v_2,v_4]\}$ because $f$ and $g$ are homomorphisms.
% Then, $\sfrac{i_1}{\sim R}$ maps $y \in Y$ to its equivalence class and likewise for $\sfrac{i_2}{\sim R}$.
% we will denote the equivalence classes in $\sfrac{X + Y}{\sim R}$ as $[x]$ and $[y]$ depending on their pre-image being either in $X$ or $Y$.
% Before we procced, we need to show that $\sfrac{i_1}{\sim R}$ and $\sfrac{i_2}{\sim R}$ are homomorphisms.
% Let $e_{x}$ be an edge in $X$ and $v_x$ is its source. We need to check that $\sfrac{i_1}{\sim R}(v_x) = (\sfrac{i_1}{\sim R};\sfrac{s_{X}}{\sim R})(e_x)$.
% $\sfrac{i_1}{\sim R}(v_x) = [v_x]$ and $(\sfrac{i_1}{\sim R};\sfrac{s_{X}}{\sim R})(e_x) = \sfrac{s_{X}}{\sim R}([e_x]) = [v_x]$ and hence $\sfrac{i_1}{\sim R}$ is a homomorphism, simialrly $\sfrac{i_2}{\sim R}$ is.
Now, the square obviously commutes.
To show that $\sfrac{X + Y}{\sim}$ is a pushout we need to argue that for each $Q$ and morphisms $j_1 = (j_{1,V}, j_{1,E})$ and $j_2 = (j_{2,V}, j_{2,E})$ such that the above square commutes there is a unique $u = (u_{V}, u_{E})$ such that $j_1 = \sfrac{i_{1}}{\sim} ; u$ and $j_2 = \sfrac{i_2}{\sim} ; u$.
We will define such $u$ as $u_{E}([i_{1,E}(e_{x})]) = j_{1,E}(e_{x})$ and $u_{E}([i_{2,E}(e_{y})]) = j_{2,E}(e_y)$ (similarly for $u_{V}$) and claim that it is a well-defined function by showing that if $t_1 \sim t_2$ then $u_{E}(t_1) = u_{E}(t_2)$.
There are three options analogoues to the proof above, so we will show the base case for $t_1 = i_{1,E}(e_{x})$ and $t_2 = i_{2,E}(e_{y})$.
$t_1 \sim t_2$ implies that there exists at least one $z$ in $E_{Z}$ such that $i_{1,E}(e_{x}) = f_{E};i_{1,E}(z)$ (or $e_{x} = f_{E}(z)$) and $[i_{1,E}(e_{x})] = \sfrac{i_{1,V}}{\sim}(e_x)$, and $e_y = g_{E}(z)$ $[in_{2,E}(e_{y})] = \sfrac{i_{2,V}}{\sim}(e_y)$.
By applying $j_{1,E}$ to the first we get $j_{1,E}(f_{E}(z)) = j_{1,E}(e_x)$ and similarly for $j_{2,E}$: $j_{2,E}(g_{E}(z)) = j_{2,E}(e_y)$ and $j_{1,E}(e_{x}) = j_{2,E}(e_{y})$ by commutativity.
Hence, $u_{E}([in_{1,E}(e_x)]) = u_{E}([in_{2,E}(e_y)])$.
% \update{Above $e_x$ and $e_y$ are different from $e_x$ and $e_y$ from the first proof, i.e. they are in $E_{X}$ and $E_{Y}$. This is probablty not good.}

Next, $u$ is a homomorphism because $j_1$ and $j_2$ are.
Finally, $u$ is unique.
Assume, that there exists $w : \sfrac{X+Y}{\sim R} \to Q$ for the same $j_1$ and $j_2$.
In order for them to commute $w_{E}([i_{1,E}(x)]) = j_1(x)$ and $w([in_{2,E}(y)]) = j_2(y)$ (similarly for $w_{V}$) which is the same as $u_{E}$.
That is, $j_1$ and $j_2$ determine $u$ uniquely.

@@

    An e-hypergraph $\mathcal{G}$ over a monoidal signature $\Sigma$ is a tuple \[(V_{\mathcal{G}},E_{\mathcal{G}},s,t,l,<_c,\#)\] where $(V_{\mathcal{G}},E_{\mathcal{G}},s,t)$ are the same as in~\ref{def:hypergraph}.
    The labelling $l$ is modified to include an extra value $\bot \;$ $l :E_{\mathcal{G}} \to \Sigma + 1$. 
    % With an abuse of notation, we will confuse $\mathcal{G}$ with $V_{\mathcal{G}} \cup E_{\mathcal{G}}$, when treating it as a set.    
    $<_c \subset (V_\mathcal{G} + E_\mathcal{G}) \times (V_\mathcal{G} + E_\mathcal{G})$ is a child relation imposing a strict partial order on $(V_\mathcal{G} + E_\mathcal{G})$.
    We require that for a given $x \in (V_\mathcal{G} + E_\mathcal{G})$ a set of all predecessors of $x\;$ $[x) = \{x' \in E_\mathcal{G} \;||\; x' <_c x\; \}$ is finite and consists of edges $e \in E_{\mathcal{G}}$ such that $l(e) = \bot$ only.
    Next, each $x$ has at most one immediate predecessor.
    We will denote the fact that $e$ is an immediate predecessor of $v$ as $e <_c^{\mu} v$.
    Similarly, a set of all successors is $(x] = \{x' \in (V_\mathcal{G} + E_\mathcal{G}) \; ||\; x <_{c} x'\}$ where $x'$ can be a node or an edge. 
    % An edge $e \in E_{\mathcal{G}}$ is unlabelled, i.e. $l(e) = \bot$ iff $(e] \not = \varnothing$.
    Finally, we require that $<_c^{\mu}$ respects connectivity, i.e. if $v \in s(e)$ then $e' <_c^{\mu} e$ iff $e' <_c^{\mu} v$.

@@

    \item \[
        \phi_{E}(<_{c,\mathcal{F}}^{\mu}(i_{V_{\mathcal{F}}}(x))) = <_{c,\mathcal{G}}^{\mu}(\phi_{V};i_{V_{\mathcal{G}}}(x))
        \] when $x$ is a node,
        and
        \[
        \phi_{E}(<_{c,\mathcal{F}}^{\mu}(i_{E_{\mathcal{F}}}(x))) = <_{c,\mathcal{G}}^{\mu}(\phi_{E};i_{E_{\mathcal{G}}}(x))  
        \] when $x$ is an edge.
        We do not require such an equation when $[x) = \varnothing$.

@@

    \begin{enumerate}
    \item $Z$ is a \textit{discrete} e-hypergraph, i.e. it has no edges.
    \item $[f_{V}(v_i)) = [f_{V}(v_j))$ and $[g_{V}(v_i)) = [g_{V}(v_j))$ for all $v_i,v_j \in V_{Z}$.
    This essentially means that $f,g$ do not map nodes to levels of different hierarchy.
    \item If $[f_{V}(v)) \not = \varnothing$ then $[g_{V}(v)) = \varnothing$ and vice versa.
    \item $\consistency^{\mu}(f(v_i)) = \consistency^{\mu}(f(v_j))$ and $\consistency^{\mu}(f(g_i)) = \consistency^{\mu}(g(v_j))$.
    \item $f$ and $g$ are mono.
    \label{pushout:assumptions}
    \end{enumerate}

@@

              Assumptions above guarantee that the predecessor of such node does not depend on the choice of $e$ if there are several of them.

@@

    % \question{In the case when images of $f$ and $g$ are top-level the function is undefined. Shall we introduce bottom?}

@@

    We will also build this relation in steps, first we do steps for nodes (1) - (3), then step (1) for edges and finally, we will interleave step (2) for edges and step (4) for nodes until fixed point.

@@

@@

    where
    \begin{enumerate}
        \item $A \in \text{obj}(\catname{EHyp_{\Sigma}})$
        \item $W, X, Y, Z$ are discrete and $f,g,h,k$ are monos
        \item The image of $f;g$ (respectively, $k;h$) consists of nodes $v$ such that $[v) = \varnothing$
    \end{enumerate}
    Since $f$ and $k$ are monos, $W$ and $Z$ are essentially subgraphs of $X$ and $Y$ and hence we will introduce the following notation which better depicts that such cospans are effectively e-hypergraphs with \textit{external} interfaces

@@

\[
    k = \langle b;p_2, f|_{Y \setminus Y_{ext}};p_1 \rangle
\]
% \[
% \begin{tikzcd}
% Y_{ext} \arrow[d] & 0 \arrow[l] \arrow[d]    \\
% Y'          & Y' \setminus Y_{ext} \arrow[l]
% \end{tikzcd}
% \]

@@

Similarly to~\ref{def:cspd} this category has a symmetric monoidal product given by a coproduct in $\catname{EHyp_{\Sigma}}$ which makes it into an SMC.
More precisely, below are cospans for tensor product and symmetry.
Tensor unit is given by the initial object in $\catname{EHyp_{\Sigma}}$.

@@

% https://q.uiver.app/#q=WzAsNSxbMCwwLCJYICsgWSJdLFsyLDAsIlggKyBZIl0sWzQsMCwiWSArIFgiXSxbNiwwLCJZICsgWCJdLFs4LDAsIlkgKyBYIl0sWzAsMSwiaWRfWCArIGlkX1kiXSxbMSwyLCJcXHNpZ21hX3tYLFl9Il0sWzQsMywiaWRfWSArIGlkX1giLDJdLFszLDIsImlkX1kgKyBpZF9YIiwyXV0=
\[
\adjustbox{scale=0.75, center}{
\begin{tikzcd}
	{X + Y} && {X + Y} && {Y + X} && {Y + X} && {Y + X}
	\arrow["{id_X + id_Y}", from=1-1, to=1-3]
	\arrow["{\sigma_{X,Y}}", from=1-3, to=1-5]
	\arrow["{id_Y + id_X}"', from=1-9, to=1-7]
	\arrow["{id_Y + id_X}"', from=1-7, to=1-5]
\end{tikzcd}
}
\]\label{morphism:symmetry}
\end{definition}

@@

\begin{remark}
    Pushout for composition is computed by first taking a coproduct of $A$ and $B$ and then identifying the nodes that share the same pre-image in $Y_{ext}$.
    Consider an example in Figure~\ref{fig:e-hyp_composition_example} below.
    The pushout is depicted in Figure~\ref{fig:e-hyp_composition_example_2}.
    New interfaces are shown in Figure~\ref{fig:e-hyp_composition_example_3}.
    They are computed as shown: a disjoint union of the input interface of the left component of the composition with the input interface of the right component of the composition except for the nodes in the image of the outermost output interface of the left component is taken.
    Similarly for the output interface.
    In particular, $\{0,1,2,3\} \uplus (\{6,7,8,9,10\} \setminus \{6\}) = \{0,1,2,3,7,8,9,10\}$.
    % The conflict and child relations in the pushout are a disjoint union of the corresponding relations from pushout components.
    Note that pushout for such composition always exists as the interface in the middle is descrete and nodes in the images of the middle interface are at the outermost level as well.
    Furthermore, $f_{ext};f$ and $g_{ext};g$ are monos and hence the span satisfies our assumptions.
\end{remark}

@@

% \update{below definition depends on whether we require the homomorphism to reflect the conflicts}

@@

\begin{figure}
    \[
    \scalebox{0.6}{
    \tikzfig{combinatorial_semantics/f_plus_g_new}
    }
    \]
    \caption{$+$ of two morphisms in $\Ecospans$}
    \label{fig:A+B}
\end{figure}

@@

% \update{We can probably omit the proofs below because they are obvious. But keeping them here serves as a sanity check.}

@@

    This category is also symmetric monoidal and has $+$.
\end{definition}

@@

@@

@@

    % \update{Can we check the proof? I haven't used all the conditions from monogamous-ness above.
    % Although, if the morphism $i+j \to L$ is mono, the complement is unique for not-monogamous hypergraphs as well.}

@@

\begin{definition}[Convex down-closed match] 
    We call $m : L \to G$ in $\catname{EHyp_{\Sigma}}$ a convex down-closed match if

    \begin{enumerate}
        \item $m$ is monomorphism
        \item $m(L)$ is a convex down-closed subgraph of $G$
        % \item \update{I've removed the requirement that consistency should be reflected because well typedness prohibits otherwise formed matches.}
    \end{enumerate}
\end{definition}

@@

% \Aleksei{Do we need to introduce substitution? This is needed if our rewrite rules are going to have variables as labels.}

@@

% Pushout example

% Consider an example below that illustrates the introduced constraints.

% \begin{remark}
%     For now, we will informally denote a combinatorial interpretation of a morphism $f$ in $\textsf{PROP}^{+}(\Sigma)$ as $[ f ]$.
% \end{remark}

% \begin{example}

% A DPOI square for rewriting in $\WellTypedMdaEcospans$ is depicted in Figure~\ref{fig:refined_dpoi}.
% A projection rule of $\llbracket f + g \rrbracket \to \llbracket f \rrbracket$ is shown in the top half of the diagram.
% The image of the matching $m$ is shown in red and its image is a convex down-closed e-hypergraph.
% Pushout complement is then computed by removing the image of $m$ from the target e-hypergraph by keeping intact the nodes that have a pre-image in the carrier of the rewriting span. The corresponding mda-cospan is depicted at the bottom: $c_i = g_i \setminus (l_i \setminus i) = \{18, 19, 1, 2, 13, 14, 5, 6, 7, 8\} \setminus (\{1,2,5,6,7,8\} \setminus \{1,2\}) = \{18, 19, 1, 2, 13, 14, 5, 6, 7, 8\} \setminus \{5,6,7,8\} = \{18,19,1,2,13,14\}$ and $c_i + j = \{18,19, 1, 2, 13, 14, 3, 4\}$ which is the input interface for $C$. Similar computations are performed for $c_o$. Then pushout glues $R$ and $C$ together along $i + j$ and the resulting interface $h_i = c_i + (r_i \setminus i) = \{18,19, 1, 2, 13, 14\} + \varnothing = \{18,19, 1, 2, 13, 14\}$ and likewise for $h_o$.

@@

% \end{example}

% \Aleksei{This figure yeilds "Dimension too large". Need to fix it.}

% This is now in soundness and completeness section

% Unlike SMC equations the equations for semilattice enriched categories are not absorbed by e-hypergraph representation and hence to further build a correspondence between $\textsf{PROP}^{+}(\Sigma)$ and $\WellTypedMdaEcospans$ we will need to turn the latter into a semilattice-enriced category.
% We already have a $+$ in $\WellTypedMdaEcospans$ so we need to require that it satisfies a particular set of equations, for example, that $h \otimes (f + g) = h \otimes f + h \otimes g$.
% \update{How to formally state this? Because $h \otimes (f+g)$ is an SMC term from $\WellTypedMdaEcospans$ which is just an SMC so far.}
% We will add such equations as DPOI rewrite rules and show that for each such rule the corresponding pushout complement and the pushout exist.

% \begin{proposition}
% Pushouts for all semilattice enrichment equations exist.

% \begin{proof}
%     Let us give a combinatorial interpretation for an instance of the first equation (distributivity) in~\ref{fig:string-equations}.
%     It can be found in Figure~\ref{fig:distributivity_interpretation}.
%     After we identify a convex down-closed image of the left-hand side of this rule within a graph $G$ we remove the image by keeping only the outermost nodes.
%     Note that because the image of all $a$'s and $b$'s are outermost nodes, we are allowed to pick any monomorphism for our pushout complement.
%     And for the same reason the pushout for the right square exists.
%     Then we simply glue the right-hand side of the rule into the hole.
%     Such equations are not absorbed by e-hypergraph representation unlike SMC equations because the right-hand side contains more edges, i.e. graphs $G$ and $H$ are not isomorphic.
%     Similar argument applies to other rules as well.
% \end{proof}
% \end{proposition}

% \update{How do we state the correspondence between term equations and their e-hypergraph counterpart without a functor?}

% \update{I think I haven't paid any attention to this fact previously, but it seems that in~\cite{Frobenius} the functor $\llbracket - \rrbracket$ is between $PROP_{\Sigma_{Frob}}$ and $Csp_{D}(Hyp_{\Sigma})$, i.e. PROP is quotiented by Frobenius equations, but they are absorbed in hypergraphs domain. We will have a similar thing: $\llbracket - \rrbracket: PROP^{+}_{\Sigma^{+}} \to \WellTypedMdaEcospans_{R^+}$, i.e. we will quotient PROP$^{+}$ by semilattice equations and quotient e-hypergraphs by the interpretation of these equations as they are not absorbed. 
% The quotienting on the left is always implicit?}

% \begin{figure}
%     \centering
%     \[
%     \scalebox{0.45}{
%     \tikzfig{combinatorial_semantics/structural_rule_pushout}}\]  
%     \caption{Distributivity rewrite rule interpretation}
%     \label{fig:distributivity_interpretation}
% \end{figure}

% \begin{definition}
%     We will denote with $\mathcal{S}$ the interpretation of the equations in~\ref{fig:string-equations} as rewrite rules in $\WellTypedMdaEcospans$.
%     In particular, for all $l = r$ in~\ref{fig:string-equations}, $\mathcal{S}$ will contain $\langle [l], [r]\rangle$ and $\langle [r], [l] \rangle$.
%     \update{Technically we add those for all possible instances of $l$ and $r$ in~\ref{fig:string-equations}.}
% \end{definition}
